% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2008 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}

% Uncomment the following lines to use the Palatino font.  Remove the
% [osf] bit if you don't like the old style figures.
%
% \usepackage[T1]{fontenc}
% \usepackage[osf]{mathpazo}

% Set your name here
\def\name{Sean O'Rourke}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {mathematics math },
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{textheight=8.5in, textwidth=6in}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Customize section headings
\usepackage{sectsty}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1em}
  }
}{
  \end{list}
}

\begin{document}

\centerline{\huge\bf \name}

\vspace{0.25in}

\begin{minipage}[t]{0.5\textwidth}
  \href{http://www.colorado.edu/}{University of Colorado Boulder } \\
  \href{http://math.colorado.edu/}{Department of Mathematics} \\
  Campus Box 395 \\
  Boulder, CO 80309-0395 
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
  Email: \href{mailto:sean.d.orourke@colorado.edu}{\tt sean.d.orourke@colorado.edu} \\
  Homepage: \href{http://math.colorado.edu/~seor3821/}{\tt http://math.colorado.edu/\char`\~seor3821/} \\
  Phone:  (303) 492-7716 \\
  Office: MATH 325 \\
\end{minipage}

\section*{Education}

\begin{itemize}
  \item Ph.D. Mathematics, University of California, Davis, 2011. 

  \item M.A. Mathematics, University of California, Davis, 2008.

  \item B.S. Mathematics, California Polytechnic State University, 2006.

\end{itemize}


\section*{Appointments \& Experience}

\begin{itemize}
	\item
	\begin{minipage}[t]{0.5\textwidth}
	University of Colorado Boulder \\
	Department of Mathematics \\
	Associate Professor 
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
	August 2021 -- Present
	\end{minipage}
	
	\item
	\begin{minipage}[t]{0.5\textwidth}
	University of Colorado Boulder \\
	Department of Mathematics \\
	Assistant Professor 
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
	August 2014 -- August 2021
	\end{minipage}

	\item 
	\begin{minipage}[t]{0.5\textwidth}
	Yale University \\
	Department of Mathematics \\
	Postdoctorate Associate 
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
	August 2012 -- July 2014
	\end{minipage}

	\item 
	\begin{minipage}[t]{0.5\textwidth}
	Rutgers University \\
	Department of Mathematics \\
	Triennial Assistant Professor of Mathematics
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
	September 2011 -- July 2012
	\end{minipage}
\end{itemize}


\subsection*{Affiliated Faculty Appointment}
\begin{itemize}
	\item
	\begin{minipage}[t]{0.5\textwidth}
	University of Colorado Boulder \\
	Department of Applied Mathematics \\
	Affiliated Faculty
	\end{minipage}
	\begin{minipage}[t]{0.5\textwidth}
	April 2017 -- Present
	\end{minipage}
\end{itemize}




\section*{Publications}
\begin{enumerate}
	\item Andrew Campbell, Sean O'Rourke and David Renfrew. 
	\newblock Universality for roots of derivatives of entire functions via finite free probability. 
	\newblock Submitted.  Available at arXiv:2410.06403, 2024. 

	\item Sean O'Rourke and Noah Williams. 
	\newblock An asymptotic refinement of the Gauss-Lucas Theorem for random polynomials with i.i.d. roots. 
	\newblock Available at arXiv:2409.09538, 2024. 

	\item Marcus Michelen and Sean O'Rourke. 
	\newblock On random polynomials with an intermediate number of real roots. 
	\newblock {\em Proceedings of the American Mathematical Society}, 152 (2024), no. 11, 4933--4942.
	
	\item Sean O'Rourke, Zhi Yin, and Ping Zhong. 
	\newblock Spectrum of Laplacian matrices associated with large random elliptic matrices.
	\newblock Submitted.  Available at arXiv:2308.16171, 2023. 

	\item Andrew Campbell, Sean O'Rourke, and David Renfrew. 
	\newblock The fractional free convolution of $R$-diagonal operators and random polynomials under repeated differentiation. 
	\newblock {\em International Mathematics Research Notices. IMRN},  2024, no. 13, 10189--10218. 
	
	\item Sean O'Rourke, Van Vu, and Ke Wang. 
	\newblock Optimal Subspace Perturbation Bounds under Gaussian Noise. 
	\newblock {\em 2023 IEEE International Symposium on Information Theory (ISIT)}, Taipei, Taiwan, 2023, pp. 2601--2606. 

	\item Andrew Campbell, Kyle Luh, and Sean O'Rourke (with an appendix by Santiago Arenas-Velilla and Victor P\'{e}rez-Abreu). 
	\newblock Extreme eigenvalues of Laplacian random matrices with Gaussian entries.  
	\newblock Submitted.  Available at arXiv:2211.17175, 2022.  

	\item Andrew Campbell and Sean O'Rourke. 
	\newblock Spectrum of L\'{e}vy-Khintchine Random Laplacian Matrices. 
	\newblock {\em Journal of Theoretical Probability},  37 (2024), no. 1, 933--973.  

	\item Isabelle Kraus, Marcus Michelen, and Sean O'Rourke.
	\newblock Sums of random polynomials with differing degrees. 
	\newblock {\em Transactions of the American Mathematical Society},  377 (2024), no. 5, 3325--3355.  
	
	\item Sean O'Rourke and Philip Matchett Wood.
	\newblock Quantitative results for banded Toeplitz matrices subject to random and deterministic perturbations. 
	\newblock {\em Linear Algebra and its Applications},  657 (2023), 50--126. 
	
	\item Richard Border, Sean O'Rourke, Teresa de Candia, Michael E. Goddard, Peter M. Visscher, Loic Yengo, Mathew Jones, and Matthew C. Keller. 
	\newblock Assortative Mating Biases Marker-based Heritability Estimators.
	\newblock {\em Nature Communications} 13, 660 (2022). 
	
	\item Andrew Campbell and Sean O'Rourke.
	\newblock Spectrum of Heavy-Tailed Elliptic Random Matrices.  
	\newblock {\em Electronic Journal of Probability}, 27 (2022), Paper No. 125, 56 pp. 
	
	\item Vishesh Jain, Indrajit Jana, Kyle Luh, and Sean O'Rourke.
	\newblock Circular law for random block band matrices with genuinely sublinear bandwidth.
	\newblock {\em Journal of Mathematical Physics}, 62, no. 8, Paper No. 083306 (2021). 
%	\item K. Luh, S. O'Rourke,
%	\emph{Eigenvectors and controllability of non-Hermitian random matrices and directed graphs}, 
%	submitted, available at {\tt arXiv:2004.10543}.  
	\item Kyle Luh and Sean O'Rourke.
	\newblock Eigenvectors and controllability of non-Hermitian random matrices and directed graphs.
	\newblock {\em Electronic Journal of Probability}, 26, Paper No. 16, 1--43 (2021). 
%	\item S. O'Rourke, N. Williams, 
%	\emph{Partial linear eigenvalue statistics for non-Hermitian random matrices}, 
%	available at {\tt arXiv:1912.08856}. 
	\item Sean O'Rourke and Noah Williams.
	\newblock Partial linear eigenvalue statistics for non-Hermitian random matrices.
	\newblock {\em Theory of Probability and its Applications}, 67 (2023), no. 4, 613--632. 
%	\item S. O'Rourke, S. Steinerberger, 
%	\emph{A Nonlocal Transport Equation Modeling Complex Roots of Polynomials under Differentiation}, 
%	submitted, available at {\tt arXiv:1910.12161}.  
	\item Sean O'Rourke and Stefan Steinerberger.
	\newblock A nonlocal transport equation modeling complex roots of polynomials under differentiation.
	\newblock {\em Proceedings of the American Mathematical Society}, 149, no. 4, 1581--1592 (2021).   
%	\item S. O'Rourke, T. R. Reddy, 
%	\emph{Sums of random polynomials with independent roots}, 
%	available at {\tt arXiv:1909.07939}.  
	\item Sean O'Rourke and Tulasi~Ram Reddy.
	\newblock Sums of random polynomials with independent roots.
	\newblock {\em Journal of Mathematical Analysis and Applications}, 495(1): 124719, 2021.  
%	\item S. O'Rourke, N. Williams, 
%	\emph{On the local pairing behavior of critical points and roots of random polynomials}, 
%	submitted, available at {\tt arXiv:1810.06781}.  
	\item Sean O'Rourke and Noah Williams.
	\newblock On the local pairing behavior of critical points and roots of random polynomials.
	\newblock {\em Electronic Journal of Probability}, 25:no. 100, 68 pp., 2020.  
%	\item K. Luh, S. O'Rourke, 
%	\emph{Eigenvector Delocalization for Non-Hermitian Random Matrices and Applications}, 
%	to appear in Random Structures \& Algorithms, available at {\tt arXiv:1810.00489}.
	\item Kyle Luh and Sean O'Rourke.
	\newblock Eigenvector delocalization for non-{H}ermitian random matrices and applications.
	\newblock {\em Random Structures \& Algorithms}, 57(1):169--210, 2020.  
%	\item N. Coston, S. O'Rourke, 
%	\emph{Gaussian fluctuations for linear eigenvalue statistics of products of independent iid random matrices}, 
%	to appear in Journal of Theoretical Probability, available at {\tt arXiv:1809.08367}.  
	\item Natalie Coston and Sean O'Rourke.
	\newblock Gaussian {F}luctuations for {L}inear {E}igenvalue {S}tatistics of {P}roducts of {I}ndependent iid {R}andom {M}atrices.
	\newblock {\em Journal of Theoretical Probability}, 33(3):1541--1612, 2020.  
%	\item S. O'Rourke, V. Vu, K. Wang,
%	\emph{Random perturbation and matrix sparsification and completion}, 
%	available at {\tt arXiv:1803.00679}.  
	\item Sean O'Rourke, Van Vu, and Ke~Wang.
	\newblock Matrices with Gaussian Noise: Optimal Estimates for Singular Subspace Perturbation. 
	\newblock {\em IEEE Transactions on Information Theory}, to appear.
%	\item P. Kopel, S. O'Rourke, V. Vu, 
%	\emph{Random matrix products: Universality and least singular values}, 
%	to appear in Annals of Probability, available at {\tt arXiv:1802.03004}.  
	\item Phil Kopel, Sean O'Rourke, and Van Vu.
	\newblock Random matrix products: Universality and least singular values.
	\newblock {\em Annals of Probability}, 48(3):1372--1410, 2020.
%	\item N. Coston, S. O'Rourke, P. Wood, 
%	\emph{Outliers in the spectrum for products of independent random matrices}, 
%	Annales de l'Institut Henri Poincar\'{e} - Probabilit\'{e}s et Statistiques, Vol. 56, No. 2 (2020), 1284--1320.  
	\item Natalie Coston, Sean O'Rourke, and Philip~Matchett Wood.
	\newblock Outliers in the spectrum for products of independent random matrices.
	\newblock {\em Annales de l'Institut Henri Poincar\'e Probabilit\'es et Statistiques}, 56(2):1284--1320, 2020.
%	\item S. O'Rourke, B. Touri, 
%	\emph{Littlewood--Offord theory and controllability of random structures}, 
%	2016 IEEE 55th Conference on Decision and Control (CDC), Las Vegas, NV, 2016, pp. 5195--5200.
	\item Sean O'Rourke and Behrouz Touri.
	\newblock Littlewood-Offord theory and controllability of random structures.
	\newblock In {\em 2016 IEEE 55th Conference on Decision and Control (CDC)}, pages 5195--5200, Dec 2016.
%	\item S. O'Rourke, N. Williams, 
%	\emph{Pairing between zeros and critical points of random polynomials with independent roots}, 
%	Transactions of the American Mathematical Society, Volume 371, Number 4 (2019), pp. 2343--2381.  
	\item Sean O'Rourke and Noah Williams.
	\newblock Pairing between zeros and critical points of random polynomials with independent roots.
	\newblock {\em Transactions of the American Mathematical Society}, 371(4):2343--2381, 2019.
%	\item S. O'Rourke, P. Wood, 
%	\emph{Low-degree factors of random polynomials}, 
%	Journal of Theoretical Probability, Volume 32, Issue 2 (2019), pp. 1076--1104.  
	\item Sean O'Rourke and Philip~Matchett Wood.
	\newblock Low-degree factors of random polynomials.
	\newblock {\em Journal of Theoretical Probability}, 32(2):1076--1104, 2019.
%	\item S. O'Rourke, V. Vu, K. Wang, 
%	\emph{Eigenvectors of random matrices: A survey}, 
%	 Journal of Combinatorial Theory, Series A, Vol. 144 (2016), 361--442. 
	\item Sean O'Rourke, Van Vu, and Ke~Wang.
	\newblock Eigenvectors of random matrices: a survey.
	\newblock {\em Journal of Combinatorial Theory. Series A}, 144:361--442, 2016.
%	\item S. O'Rourke, B. Touri, 
%	\emph{On a conjecture of Godsil concerning controllable random graphs}, 
%	SIAM J. Control Optim. Vol. 54, No. 6 (2016), pp. 3347--3378.  
	\item Sean O'Rourke and Behrouz Touri.
	\newblock On a conjecture of {G}odsil concerning controllable random graphs.
	\newblock {\em SIAM Journal on Control and Optimization}, 54(6):3347--3378, 2016.
%	\item S. O'Rourke, P. Wood, 
%	\emph{Spectra of nearly Hermitian random matrices}, 
%	Annales de l'Institut Henri Poincar\'{e} - Probabilit\'{e}s et Statistiques, Vol. 53, No. 3 (2017), 1241--1279.
	\item Sean O'Rourke and Philip~Matchett Wood.
	\newblock Spectra of nearly {H}ermitian random matrices.
	\newblock {\em Annales de l'Institut Henri Poincar\'e Probabilit\'es et Statistiques}, 53(3):1241--1279, 2017.

%	\item  S. O'Rourke, B. Touri, 
%	\emph{Controllability of random systems: Universality and minimal controllability}, 
%	submitted, available at {\tt arXiv:1506.03125}.
	\item Sean O'Rourke and Behrouz Touri.
	\newblock Controllability of random systems: Universality and minimal controllability.
	\newblock Available at  arXiv:1506.03125, 2015.  
%	\item  S. O'Rourke, 
%	\emph{Critical points of random polynomials and characteristic polynomials of random matrices}, 
%	International Mathematics Research Notices, Vol. 2016, No. 18 (2016), pp. 5616--5651. 
	\item Sean O'Rourke.
	\newblock Critical points of random polynomials and characteristic polynomials of random matrices.
	\newblock {\em International Mathematics Research Notices. IMRN}, (18):5616--5651, 2016.

%	\item S. O'Rourke, D. Renfrew, 
%	\emph{Central limit theorem for linear eigenvalue statistics of elliptic random matrices}, 
%	Journal of Theoretical Probability, Volume 29, Issue 3 (2016), pp. 1121--1191.  
	\item Sean O'Rourke and David Renfrew.
	\newblock Central limit theorem for linear eigenvalue statistics of elliptic random matrices.
	\newblock {\em Journal of Theoretical Probability}, 29(3):1121--1191, 2016.
%	\item S. O'Rourke, D. Renfrew, A. Soshnikov, V. Vu, 
%	\emph{Products of independent elliptic random matrices}, 
%	J. Stat. Phys. Vol. 160, No. 1 (2015), 89--119.  
	\item Sean O'Rourke, David Renfrew, Alexander Soshnikov, and Van Vu.
	\newblock Products of independent elliptic random matrices.
	\newblock {\em Journal of Statistical Physics}, 160(1):89--119, 2015.
%	\item S. O'Rourke, V. Vu, K. Wang, 
%	\emph{Random perturbation of low rank matrices: Improving classical bounds}, 
%	Linear Algebra and its Applications, Volume 540 (2018), pp. 26--59.  
	\item Sean O'Rourke, Van Vu, and Ke~Wang.
	\newblock Random perturbation of low rank matrices: improving classical bounds.
	\newblock {\em Linear Algebra and its Applications}, 540:26--59, 2018.
%	\item S. O'Rourke, D. Renfrew, 
%	\emph{Low rank perturbations of large elliptic random matrices}, 
%	Electronic Journal of Probability Vol. 19, No. 43, 1--65 (2014).
	\item Sean O'Rourke and David Renfrew.
	\newblock Low rank perturbations of large elliptic random matrices.
	\newblock {\em Electronic Journal of Probability}, 19:no. 43, 65 pp., 2014.
%	\item H. Nguyen, S. O'Rourke,
%	\emph{On the concentration of random multilinear forms and the universality of random block matrices},
%	Probability Theory and Related Fields, Volume 162, Issue 1-2, pp 97--154 (2015). 
	\item Hoi~H. Nguyen and Sean O'Rourke.
	\newblock On the concentration of random multilinear forms and the universality of random block matrices.
	\newblock {\em Probability Theory and Related Fields}, 162(1-2):97--154, 2015.
%	\item S. O'Rourke, V. Vu,
%	\emph{Universality of local eigenvalue statistics in random matrices with external source},
%	Random Matrices: Theory and Applications, Vol. 3, No. 2 (2014).
	\item Sean O'Rourke and Van Vu.
	\newblock Universality of local eigenvalue statistics in random matrices with external source.
	\newblock {\em Random Matrices: Theory and Applications}, 3(2):1450005, 37 pp., 2014.
%	\item S. O'Rourke, A. Soshnikov,
%	\emph{Partial linear eigenvalue statistics for Wigner and sample covariance random matrices},
%	J. Theor. Probab. Vol. 28, No. 2 (2015), 726--744. 
	\item Sean O'Rourke and Alexander Soshnikov.
	\newblock Partial linear eigenvalue statistics for {W}igner and sample covariance random matrices.
	\newblock {\em Journal of Theoretical Probability}, 28(2):726--744, 2015.
%	\item H. Nguyen, S. O'Rourke,
%	\emph{The elliptic law},
%	International Mathematics Research Notices Vol. 2015, No. 17 (2015), pp. 7620--7689.   
	\item Hoi~H. Nguyen and Sean O'Rourke.
	\newblock The elliptic law.
	\newblock {\em International Mathematics Research Notices. IMRN}, (17):7620--7689, 2015.
%	\item S. O'Rourke, 
%	\emph{A note on the Marchenko-Pastur law for a class of random matrices with dependent entries}, 
%	Electronic Communications in Probability, Vol. 17, Art. 28, pp. 1--13 (2012). 
	\item Sean O'Rourke.
	\newblock A note on the {M}archenko-{P}astur law for a class of random matrices with dependent entries.
	\newblock {\em Electronic Communications in Probability}, 17:no. 28, 13 pp., 2012.
%	\item S. O'Rourke, 
%	\emph{Fluctuations of Matrix Entries of Analytic Functions of Non-Hermitian Random Matrices}, 
%	Random Matrices: Theory and Applications, Vol. 1, No. 3 (2012).
	\item Sean O'Rourke.
	\newblock Fluctuations of matrix entries of analytic functions of non-{H}ermitian random matrices.
	\newblock {\em Random Matrices: Theory and Applications}, 1(3):1250008, 22 pp., 2012.
%	\item S. O'Rourke, D. Renfrew, A. Soshnikov,  
%	\emph{Fluctuations of Matrix Entries of Regular Functions of Sample Covariance Random Matrices}, 
%	Theory Probab. Appl. Vol. 58, No. 4, pp. 615--639 (2014). 
	\item Sean O'Rourke, David Renfrew, and Alexander Soshnikov.
	\newblock Fluctuations of matrix entries of regular functions of sample covariance random matrices.
	\newblock {\em Theory of Probability and its Applications}, 58(4):615--639, 2014.
%	\item S. O'Rourke, D. Renfrew, A. Soshnikov, 
%	\emph{On Fluctuations of Matrix Entries of Regular Functions of Wigner Matrices with Non-Identically Distributed Entries}, 
%	J. Theor. Probab. Vol. 26, No. 3 (2013), 750--780.
	\item Sean O'Rourke, David Renfrew, and Alexander Soshnikov.
	\newblock On fluctuations of matrix entries of regular functions of {W}igner matrices with non-identically distributed entries.
	\newblock {\em Journal of Theoretical Probability}, 26(3):750--780, 2013.
%	\item S. O'Rourke, A. Soshnikov,  
%	\emph{Products of Independent Non-Hermitian Random Matrices}, 
%	Electronic Journal of Probability, Vol. 16, Art. 81, 2219--2245 (2011).
	\item Sean O'Rourke and Alexander Soshnikov.
	\newblock Products of independent non-{H}ermitian random matrices.
	\newblock {\em Electronic Journal of Probability}, 16:no. 81, 2219--2245, 2011.
%	\item P. Dueck, S. O'Rourke, D. Renfrew, A. Soshnikov, 
%	\emph{Spectral Properties of Large Random Matrices with Independent Entries}, 
%	Noncommutative Harmonic Analysis with Applications to Probability III. Banach Center Publ. Vol. 96, 115--134 (2012).
	\item Pierre Dueck, Sean O'Rourke, David Renfrew, and Alexander Soshnikov.
	\newblock Spectral properties of large random matrices with independent entries.
	\newblock In {\em Noncommutative harmonic analysis with applications to probability {III}}, volume~96 of {\em Banach Center Publ.}, pages 115--134. Polish Acad. Sci. Inst. Math., Warsaw, 2012.
%	\item S. O'Rourke, 
%	\emph{Gaussian Fluctuations of Eigenvalues in Wigner Random Matrices}, 
%	J. Stat. Phys. Vol. 138, No. 6 (2010), 1045--1066.
	\item Sean O'Rourke.
	\newblock Gaussian fluctuations of eigenvalues in {W}igner random matrices.
	\newblock {\em Journal of Statistical Physics}, 138(6):1045--1066, 2010.
\end{enumerate}

\section*{Honors, Awards, \& Grants}
\begin{itemize}
	\item PI of National Science Foundation (NSF) grant No. DMS-2143142, CAREER: Beyond Independence: Random Matrices and Applications, 2022--2027, \$430,164.00.  
	\item PI of National Science Foundation (NSF) grant No. DMS-1810500, Eigenvectors of Large-Dimensional Random Matrices and Graphs, 2018--2023, \$81,533.00.  
	\item Co-PI of National Science Foundation (NSF) grant No. ECCS-1610003, Stochastic Approach to Control of Large Scale Networks, 2016--2019, \$296,558.00 (PI: Behrouz Touri).  
	\item AMS-Simons Travel Grant, July 2012 -- June 2015.
	\item Henry L. Alder Prize for Excellence in Teaching, University of California, Davis, 2010.
	\item VIGRE Summer Research Fellowship, University of California, Davis, Summer 2010.
	\item VIGRE Research Fellowship, University of California, Davis, Winter 2010.
	\item VIGRE Summer Research Fellowship, University of California, Davis, Summer 2009.
	\item VIGRE Research Fellowship, University of California, Davis, Spring 2009.
	\item VIGRE Research Fellowship, University of California, Davis, Spring 2008.
	\item Outstanding Mathematics Senior, California Polytechnic State University, 2006.
	\item Dean's List, California Polytechnic State University, 2002 -- 2006.
\end{itemize}


\section*{Presentations \& Posters}
\begin{itemize}
	\item Invited talk at the AMS Fall Western Sectional Meeting Special Session ``Random matrices, related structures, and applications,'' October 2024.
	\item Invited talk at the Institute for Computational and Experimental Research in Mathematics (ICERM) hot topic workshop ``Random Matrices and Applications,'' May 2024. 
	\item Talk at the 2024 Rocky Mountain Section meeting of the MAA special session ``Random Matrices and Free Probability Theory,'' April 2024. 
	\item Invited talk at the Canadian Discrete and Algorithmic Mathematics Conference (CanaDAM) mini-symposium ``Random matrix theory and connections,'' June 2023. 
	\item Invited talk at the University of Illinois at Chicago (UIC) Probability and Combinatorics Seminar, April 2023. 
	\item Invited talk at the University of Denver Analysis and Dynamics Seminar, November 2022.  
	\item Invited tutorial talks at the Conference on Random Matrix Theory and Numerical Linear Algebra, University of Washington, June 2022.  
	\item Invited tutorial talks at the Random Matrix EurAsia 2022 Workshop (held virtually), May 2022.  
	\item Invited talk at the Random Matrix EurAsia 2022 Workshop (held virtually), April 2022.  
	\item Invited talk at the University of Illinois at Chicago (UIC) Probability and Combinatorics Seminar, November 2021.  
	\item Invited talk at the University of M\"{u}nster Probability Seminar, October 2021.
	\item Invited talk at the AMS Fall Southeastern Sectional Meeting Special Session ``Polynomials, Approximation Theory, and Potential Theory,'' October 2020.  
	\item Contributed (virtual prerecorded) talk at the Bernoulli-IMS One World Symposium Special Session ``Random matrices,'' August 2020.  
	\item Invited talk at the AMS Fall Western Sectional Meeting Special Session ``Random Matrices and Related Structures,'' November 2019.  
	\item Invited talk at the Yale University Analysis-Combinatorics Joint Seminar, October 2019.  
	\item Invited talk at the Workshop on High-Dimensional Covariance Operators and their Applications, Humboldt University, Berlin, September 2019.  
	\item Invited talk at the University of California, Irvine Probability Seminar, May 2019.  
	\item Invited talk at the Georgia Institute of Technology High Dimensional Seminar, April 2019.  
	\item Invited talk at the Harvard University Random Matrix \& Probability Theory Seminar, November 2018.  
	\item Invited talk at the Princeton University Topics in Probability Seminar, November 2018.  
	\item Invited talk at the AMS Fall Central Sectional Meeting Special Session ``Random Matrix Theory Beyond Wigner and Wishart,'' October 2018.  
	\item Invited talk at the Sums \& Products of Random Matrices workshop at the ZiF Center for Interdisciplinary Research, Bielefeld University, Germany, August 2018.
	\item Invited talk at the Case Western Reserve University Department of Mathematics, Applied Mathematics and Statistics Colloquium, April 2018.  
	\item Invited talk at the Colorado State University Applied Mathematics Seminar, March 2018.  
	\item Invited talk at the University of Colorado Boulder Applied Mathematics Stochastics Seminar, November 2017.  
	\item Invited talk at the AMS Fall Western Sectional Meeting Special Session ``Random Matrices: Theory and Applications,'' November 2017.  
	\item Invited talk at the University of California, San Diego Electrical and Computer Engineering Colloquium, November 2017.  
	\item Invited talk at the University of Colorado Boulder Applied Mathematics Colloquium, October 2016.  
	\item Invited session talk at the World Congress in Probability and Statistics hosted by the Fields Institute, Toronto, July 2016.
	\item Invited talk at the Ohio State University Combinatorics and Probability Seminar, June 2016.
	\item Invited talk at the AMS Spring Western Sectional Meeting Special Session ``Topics in Probability,'' April 2016.  
	\item Invited talk at the University of Denver Analysis and Dynamics Seminar, November 2015.  
	\item Minisymposium talk at the 2015 SIAM Conference on Applied Linear Algebra, October 2015.  
	\item Invited talk at the University of Colorado Colorado Springs (UCCS) Department of Mathematics Colloquium, September 2015.
	\item Invited talk at the Random Matrices, Random Growth Processes and Statistical Physics Workshop at the Simons Center for Geometry and Physics, September 2015.
	\item Contributed talk at the $17$th International Conference on Random Structures and Algorithms (RS\&A2015) at Carnegie Mellon University, July 2015.
	\item Invited talk at the University of Colorado Boulder Probability Seminar, February 2015.  
	\item Invited talk at the University of Wisconsin-Madison Probability Seminar, September 2014.  
	\item Invited talk at the ICERM Workshop on Eigenvectors in Graph Theory and Related Problems in Numerical Linear Algebra, May 2014.
	\item Invited talk at the Temple University Probability Seminar, April 2014.  
	\item Invited talk at the University of Michigan Analysis/Probability Seminar, April 2014.
	\item Invited talk at the University of Virginia Harmonic Analysis and PDEs Seminar, March 2014.	
	\item Invited talk at the University of Mississippi Department of Mathematics, January 2014.
	\item Invited talk at the University of Massachusetts Amherst Department of Mathematics and Statistics, January 2014.
	\item Invited talk at Indiana University Bloomington Department of Mathematics, January 2014.
	\item Invited talk at the University of Connecticut Department of Mathematics, January 2014.
	\item Invited talk at the University of Rochester Department of Mathematics, January 2014.
	\item Invited talk at the 2014 Joint Mathematics Meetings AMS Special Session on Random Matrices, January 2014.
	\item Invited talk at the University of Colorado Boulder Department of Mathematics, December 2013.
	\item Contributed talk at the $36$th Conference on Stochastic Processes and their Applications, August 2013.
	\item Invited talk at the University of California, Los Angeles Participating Analysis Seminar, March 2013.  
	\item Invited talk at the Yale University Combinatorics and Probability Seminar, November 2012.  
	\item Poster presentation for the Random Matrix Workshop at Hausdorff Center for Mathematics, May 2012.
	\item Invited talk at the University of Pennsylvania Combinatorics and Probability Seminar, April 2012.
	\item Invited talk at the University of Colorado Boulder Probability Seminar, March 2012.
	\item Invited talk at the University of California, Davis Mathematical Physics \& Probability Seminar, February 2011.  
	\item Invited talk at the University of Alberta Department of Mathematical and Statistical Sciences, January 2011.  
	\item Short talk at the Arizona School of Analysis with Applications, March 2010.
	\item Poster presentation at the V Brunel Workshop on Random Matrix Theory, December 2009.
	\item Talk at the University of California, Davis Student-Run Math Seminar, October 2009.
	\item Talk at the University of California, Davis Student-Run Discrete Math Seminar, November 2007.
\end{itemize}
 


\section*{Teaching Experience}
\subsection*{Courses Taught at the University of Colorado Boulder}

   \begin{tabular}{r l}
   	{\bf Spring 2025}: & MATH 4650: Intermediate Numerical Analysis 1 \\
			&  MATH 6350: Functions of a Complex Variable 1 \\
   	{\bf Fall 2024}: & MATH 3001: Analysis 1 \\
   	{\bf Spring 2024}: & MATH 3001: Analysis 1 \\
			& MATH 4530: Foundations of Data Science \\
   	{\bf Fall 2023}: & MATH 6534: Topics in Mathematical Probability \\
   	{\bf Spring 2022}: & MATH 3001: Analysis 1 \\
   	{\bf Fall 2021}: & MATH 6310: Introduction to Real Analysis 1 \\
         {\bf Spring 2021}: & MATH 3001: Analysis 1 \\
   	{\bf Fall 2020}: & FYSM (First Year Seminar): Impossible or Implausible: Paradoxes and Puzzles \\
			     & MATH 6350: Functions of a Complex Variable 1 \\
   	{\bf Spring 2020}: & MATH 2400: Calculus 3 (course coordinator and instructor for $2$ sections)  \\
   	{\bf Spring 2019}: & MATH 4520: Introduction to Mathematical Statistics \\
   	{\bf Fall 2018}: & FYSM (First Year Seminar): Impossible or Implausible: Paradoxes and Puzzles \\
   	{\bf Spring 2018}: & MATH 4520: Introduction to Mathematical Statistics \\
				& MATH 6320: Introduction to Real Analysis 2 \\
   	{\bf Fall 2017}: & MATH 4510: Introduction to Probability Theory \\
   	{\bf Fall 2016}: & MATH 6350: Functions of a Complex Variable 1 \\
   	{\bf Spring 2016}: & MATH 3001: Analysis 1 \\
				& MATH 4520: Introduction to Mathematical Statistics \\
   	{\bf Fall 2015}: & MATH 6310: Introduction to Real Analysis 1 \\
   	{\bf Spring 2015}: & MATH 3001: Analysis 1 \\
				& MATH 4510: Introduction to Probability Theory \\
   	{\bf Fall 2014}: &  MATH 6534: Topics in Mathematical Probability
   \end{tabular}
   
   \subsection*{Undergraduate Student Independent Study at the University of Colorado Boulder}
   \begin{tabular}{r l}
   	{\bf Spring 2025}: & The Probabilistic Method.  Melanie Fouque  \\
   	{\bf Spring 2022}: & Enumerative Combinatorics.  Lex Bradford \\
   	{\bf Spring 2021}: & Controllability of Random Graph Laplacians (cont.). Kyle Schneider \\
   	{\bf Fall 2020}: & Controllability of Random Graph Laplacians. Kyle Schneider \\
   	{\bf Fall 2019}: & Random Graphs (cont.).  Poramate Nakkirt \\
   	{\bf Spring 2019}: & Random Graphs.  Poramate Nakkirt  \\
   				& Random Polynomials.  Megan Collins \\
   	{\bf Spring 2018}: & Spectral Properties of Random Graphs.  Megan Sochinski \\
   				& The Probabilistic Method.  Ian Gossett
   \end{tabular}
   
%   \begin{itemize}
%   \item {\bf Fall 2019}: Random Graphs (cont.).  Poramate Nakkirt
%   \item {\bf Spring 2019}: Random Graphs.  Poramate Nakkirt 
%   \item {\bf Spring 2019}: Random Polynomials.  Megan Collins 
%   \item {\bf Spring 2018}: Spectral Properties of Random Graphs.  Megan Sochinski 
%   \item {\bf Spring 2018}: The Probabilistic Method.  Ian Gossett
%   \end{itemize}
   
   \subsection*{Graduate Student Independent Study at the University of Colorado Boulder}
   \begin{tabular}{r l}
   	{\bf Spring 2024}: & Random Matrix Theory. Jackson Carpenter  \\
			&High dimensional Probability. Wilson Wu \\
   	{\bf Fall 2023}: & Topics in Random Matrix Theory. Calum Shearer  \\
			& Random Matrix Theory. Aidan Powers \\
	{\bf Spring 2023}: & Topics in Random Matrix Theory. Jackson Carpenter  \\
   	{\bf Spring 2019}: & Probability Theory.  Sangman Lee, Joel Ornstein, and Yu Wang \\
   	{\bf Fall 2018}: & Entries of Functions of Random Matrices.  Shumin Zeng \\
   			& Random Matrix Theory.  Andrew Campbell \\
   	{\bf Spring 2015}: & Markov Chains and Mixing Times.  Natalie Coston and Noah Williams 
   \end{tabular} 
   
%   \begin{itemize}
%   \item {\bf Spring 2019}: Probability Theory.  Sangman Lee, Joel Ornstein, and Yu Wan
%   \item {\bf Fall 2018}: Entries of Functions of Random Matrices.  Shumin Zeng 
%   \item {\bf Fall 2018}: Random Matrix Theory.  Andrew Campbell 
%   \item {\bf Spring 2015}: Markov Chains and Mixing Times.  Natalie Coston and Noah Williams 
%   \end{itemize}
   
%   \begin{itemize}
%   \item Undergraduate student independent study: Ian Gossett (Spring 2018), Megan Sochinski (Spring 2018), Megan Collins (Spring 2019), Poramate Nakkirt (Spring 2019 and Fall 2019).
%   \item Graduate student independent study: Natalie Coston (Spring 2015), Noah Williams (Spring 2015), Andrew Campbell (Fall 2018), Shumin Zeng (Fall 2018), Sangman Lee (Spring 2019), Joel Ornstein (Spring 2019), Yu Wang (Spring 2019).  
%   \end{itemize}
   

 
   
   
   
\subsection*{Courses Taught at Rutgers University}   
   \begin{tabular}{r l}
   	{\bf Spring 2012}: & Multivariable Calculus \\
			     	& Mathematical Theory of Statistics \\
	{\bf Fall 2011}: & Introductory Linear Algebra \\
				& Multivariable Calculus
   \end{tabular}

\subsection*{Courses Taught at the University of California, Davis}
    \begin{tabular}{r l}
    	{\bf Summer 2011}: & Linear Algebra \\
	{\bf Fall 2010}: & Differential Calculus \\
	{\bf Spring 2010}: & Calculus for Biology and Medicine \\
	{\bf Fall 2009}: & Trigonometry \\
	{\bf Fall 2008}: & Precalculus \\
	{\bf Summer 2008}: & Linear Algebra \\
	{\bf Fall 2007}: & Trigonometry \\
	{\bf Summer 2007}: & Vector Analysis
   \end{tabular}



\section*{Supervision}

\subsection*{Completed Doctoral Graduate Students}
\begin{itemize}
	\item Andrew Campbell, Ph.D. May 2023 \\
	Thesis: \textit{Spectral Properties of Random Matrices with Dependent Entries}
	\item Ali Lotfi, Ph.D. May 2022 (co-advised with Prof.\  Julien Langou) \\
	Thesis: \textit{Numerical Stability of the GSXO Orthogonalization Scheme}
	\item Noah Williams, Ph.D. May 2019 \\
	Thesis: \textit{On the pairing between zeros and critical points of random polynomials with independent roots}
	\item Natalie Coston, Ph.D. May 2018 \\
	Thesis: \textit{Spectral Properties of Products of Independent Random Matrices}
\end{itemize}
	
	
\subsection*{Current Doctoral Graduate Students}
\begin{itemize}
	\item Jackson Carpenter, candidate
	\item Isabelle Kraus, candidate
	\item Calum Shearer, candidate 
\end{itemize}

\subsection*{Completed Masters' Students}
\begin{itemize}
	\item Yuwei Jia, M.A. 2021 \\
	Presentation: \textit{Estimating covariance matrices} 
	\item Shumin Zeng, M.A. 2018 \\
	Presentation: \textit{Matrix entries of analytic functions of random matrices}
\end{itemize}

%\subsection*{Current Master's Students}

\subsection*{Postdoctoral Scholars}
\begin{itemize}
	\item Nhan Nguyen, 2023--Present
	\item Philip Kopel, 2016--2018
\end{itemize}

\subsection*{Summer Research Experience Supervision}
   \begin{tabular}{r p{4.65in}}
   {\bf Summer 2024}: & Derivatives of Random Polynomials (co-organized with Kyle Luh) \\
   & Jeff (JJ) Calhoun (CU undergraduate student), Mazzy Fennell (CU undergraduate student), Edouard Heitzmann (CU graduate student), Ellie Le (CU undergraduate student), Asa Morrison (CU undergraduate student), Tony Samour (CU undergraduate student) \\
   {\bf Summer 2022}: & Roots and critical points of random polynomials \\
   & Omar Almutawa (CU undergraduate), Lex Bradford (CU undergraduate), Jackson Carpenter (CU graduate student), Nicholas Christoffersen (CU graduate student), Charlotte Crotwell (CU graduate student),  Zee Culwell (CU undergraduate), Tianna Juarez (CU undergraduate) \\
   {\bf Summer 2020}: & Sums of random polynomials \\
   & Gabriel Lopez (CU graduate student), Levi Lorenzo (CU graduate student), Franny McWilliams (CU undergraduate), Kyle Schneider (CU undergraduate) \\
   {\bf Summer 2019}: & Sums of random polynomials (as part of the CU Science Discovery STEM Research Experience Program) \\
   & Arjun Ramani (high school student), Eojin Lee (high school student) \\
   {\bf Summer 2018}: & Invertible random matrices \\
   & David Atkinson (CU undergraduate), Andrew Campbell (CU graduate student), Megan Collins (CU undergraduate), Christopher Dudley (CU undergraduate), Yueqi Pan (CU undergraduate) \\
   {\bf Summer 2016}: & Critical points of random polynomials and random matrices \\
   & Krisztina Dearborn (CU graduate student), Ian Gossett (CU undergraduate), Shen Lu  (CU graduate student), Isaac Vance (CU undergraduate), Katherine Zagnoli (CU undergraduate), Shumin Zeng (CU undergraduate)
   \end{tabular}
   
\subsection*{Summer Math Academy}
 \begin{tabular}{r p{4.65in}}
   {\bf Summer 2024}: & Math academy and video game design summer course \\
   & Two week course on advanced mathematics and video game design for high school students as part of the CU Science Discovery program.   Supervised $9$ high school participants as well as $2$ TAs.  \\
   {\bf Summer 2023}: & Math academy and video game design summer course \\
   & Two week course on advanced mathematics and video game design for high school students as part of the CU Science Discovery program.   Supervised $10$ high school participants as well as $3$ TAs. 
   \end{tabular}
   
\subsection*{Undergraduate Honors Thesis Supervision}
\begin{itemize}
	\item Kyle Schneider - magna cum laude, May 2021 \\
	Thesis: \textit{Uncontrollable Networks for Laplacian Leader-Follower Dynamics}
	\item Megan Collins - summa cum laude, May 2020 \\
	Thesis: \textit{Distribution and Properties of the Critical Values of Random Polynomials with Non-Independent and Non-Identically Distributed Roots}
	\item Poramate Nakkirt - magna cum laude, December 2019 \\
	Thesis: \textit{Limiting Moments of the Eigenvalue Distribution of the Watts--Strogatz Random Graph}
	\item Megan Sochinski - magna cum laude, May 2018 \\  
	Thesis: \textit{Finding Planted Cliques in Erd\H{o}s--R\'{e}nyi Random Graphs: Improving previous methods and expanding applications} 
\end{itemize}


\section*{Conference \& Workshop Participation}
\begin{itemize}
	\item (Upcoming) Second Conference on Random Matrix Theory and Numerical Linear Algebra, June 2025. 
	\item 2024 Rocky Mountain Section meeting of the MAA, April 2024. 
	\item Conference on Random Matrix Theory and Numerical Linear Algebra at the University of Washington, June 2022.  
	\item Random Matrix EurAsia 2022, May 2022.
	\item 2022 Joint Mathematics Meetings, April 2022.
	\item 2020 Joint Mathematics Meetings, January 2020.  
	\item AMS Fall Western Sectional Meeting, November 2019.  
	\item High-Dimensional Covariance Operators and their Applications at Humboldt University, Berlin, September 2019.  
	\item $41$st Stochastic Processes and their Applications Conference, July 2019.
	\item AMS Fall Central Sectional Meeting, October 2018.  
	\item Sums \& Products of Random Matrices workshop at the ZiF Center for Interdisciplinary Research, Bielefeld University, Germany, August 2018.
	\item AMS Fall Western Sectional Meeting, November 2017.  
	\item AMS Fall Western Sectional Meeting, October 2016.  
	\item World Congress in Probability and Statistics hosted by the Fields Institute, Toronto, July 2016.  
	\item AMS Spring Western Sectional Meeting, April 2016.  
	\item SIAM Conference on Applied Linear Algebra, October 2015.
	\item Random Matrices, Random Growth Processes and Statistical Physics Workshop at the Simons Center for Geometry and Physics, September 2015.
	\item $17$th International Conference on Random Structures and Algorithms (RS\&A2015) at Carnegie Mellon University, July 2015.
	\item ICERM Workshop on Eigenvectors in Graph Theory and Related Problems in Numerical Linear Algebra, May 2014.
	\item 2014 Joint Mathematics Meetings, January 2014.
	\item $36$th Conference on Stochastic Processes and their Applications, August 2013.
	\item AMS Short Course on Random Matrices at the 2013 Joint Mathematics Meetings, January 2013.
	\item Random Matrix Workshop at the Hausdorff Center for Mathematics, May 2012.
	\item $105$th Statistical Mechanics Conference, May 2011.  
	\item Random Matrices Workshop at the American Institute of Mathematics, December 2010.
	\item Random Matrix Theory and its Applications II Workshop at MSRI, December 2010.
	\item Random Matrix Theory and its Applications I Workshop at MSRI, September 2010.
	\item Arizona School of Analysis with Applications, March 2010.
	\item V Brunel Workshop on Random Matrix Theory, December 2009.
	\item Random Matrix Theory Graduate Workshop at MSRI, July 2009.
\end{itemize}


\section*{Service \& Leadership}
\subsection*{Service to the Department of Mathematics at the University of Colorado Boulder} 
\begin{itemize}
	\item Primary Unit Evaluation Committee for Assistant Professor Kyle Luh's Comprehensive Review (Fall 2024) (chair). 
	\item Faculty hiring committee (Fall 2023). 
	\item Associate Chair for Undergraduate Studies (Spring 2022). 
	\item Kempner Colloquium Organizer (August 2015 -- May 2022; January 2024 -- July 2024).   
	\item Probability Seminar Organizer (August 2014 -- Present).
	\item Undergraduate Committee (August 2014 -- July 2015; August 2017 -- July 2018; August 2019 -- July 2022; August 2023 -- Present).
	\item Primary Unit Evaluation Committee for Assistant Professor Agn\'{e}s Beaudry's Tenure and Promotion to Associate Professor (Fall 2021).
	\item Primary Unit Evaluation Committee for Dr.\ Albert Bronstein's Reappointment as Instructor (Fall 2020). 
	\item Faculty mentor to Kyle Luh (August 2020 -- Present). 
	\item Course Coordinator, Calculus 3, 13 sections (Spring 2020).  
	\item Faculty Hiring Committee (September 2019 -- January 2020).
	\item Committee for Lower Division Curriculum Matters (August 2018 -- July 2019).  
	\item Diversity Committee (August 2016 -- July 2017).  
	\item Analysis Preliminary Examination Committees for Fall 2015, Fall 2016, Fall 2018, Fall 2020, Spring 2024, and Spring 2025 exams.  
\end{itemize}

\subsection*{Service to Other Departments at the University of Colorado Boulder} 
\begin{itemize}
	\item Department of Electrical, Computer and Energy Engineering Faculty Search Committee (September 2017 -- April 2018).
\end{itemize}

\subsection*{Service to the University of Colorado Boulder} 
\begin{itemize}
	\item Advisory Board for the First Year Seminar Program (Fall 2020). 
\end{itemize}

\subsection*{Ph.D. Dissertation Committees at the University of Colorado Boulder} 
\begin{itemize}
	\item Isabelle Kraus, Department of Mathematics, Fall 2024 (advisor)
	\item Charlie Carlson, Department of Computer Science, Summer 2023
	\item Daniel Ferguson, Department of Applied Mathematics, Summer 2022
	\item Krisztina Dearborn, Department of Mathematics, Summer 2022
	\item Ali Lotfi, Department of Mathematics, Spring 2022 (advisor)
	\item Zhe Feng, Department of Electrical, Computer and Energy Engineering, Spring 2021
	\item Albany Thompson, Department of Mathematics, Spring 2021
	\item Braden Balentine, Department of Mathematics, Spring 2021
	\item Zhenhua Wang, Department of Mathematics, Spring 2020 
	\item Saeed Khalili, Department of Mathematics, Fall 2019 
	\item Noah Williams, Department of Mathematics, Spring 2019 (advisor)
	\item Natalie Coston, Department of Mathematics, Spring 2018 (advisor) 
	\item Peter Willis, Department of Applied Mathematics, Spring 2018 
	\item Ian Long, Department of Mathematics, Fall 2017
\end{itemize}

\subsection*{Master's Defense Committees at the University of Colorado Boulder} 
\begin{itemize}
	\item Yuwei Jia, Department of Mathematics, Fall 2021 (advisor)
	\item Richard Dyer, Department of Mathematics, Fall 2018 
	\item Shumin Zeng, Department of Mathematics, Fall 2018 (advisor) 
	\item Isabel Corona, Department of Mathematics, Spring 2018 
	\item Kellin Pelrine, Department of Mathematics, Spring 2018 
	\item Brendt Gerics, Department of Mathematics, Spring 2018
	\item Patrick Normile, Department of Mathematics, Spring 2016 
	\item Xiaorong Lie, Department of Mathematics, Spring 2016 
\end{itemize}

\subsection*{Undergraduate Honors Thesis Committees at the University of Colorado Boulder} 
\begin{itemize}
	\item Kyle Schneider, Department of Mathematics, Spring 2021 (advisor)
	\item Megan Collins, Department of Mathematics, Spring 2020 (advisor)
	\item Poramate Nakkirt, Department of Mathematics, Fall 2019 (advisor)
	\item Megan Sochinski, Department of Mathematics, Spring 2018 (advisor)
	\item Manna Chen, Department of Economics, Spring 2016 
\end{itemize}

\subsection*{Comprehensive Examination Committees at the University of Colorado Boulder} 
\begin{itemize}
	\item Benjamin Kitchen, Department of Mathematics, Fall 2024
	\item Nicholas Christoffersen, Department of Mathematics, Fall 2023
	\item Daniel Ferguson, Department of Applied Mathematics, Fall 2021
	\item Peter Rock II, Department of Mathematics, Fall 2021
	\item Ian Miller, Department of Mathematics, Spring 2021
	\item Isabelle Kraus, Department of Mathematics, Fall 2020 (advisor)
	\item Zhe Feng, Department of Electrical, Computer and Energy Engineering, Fall 2019  
	\item Andrew Campbell, Department of Mathematics, Spring 2019 (advisor) 
	\item Albany Thompson, Department of Mathematics, Fall 2018 
	\item Krisztina Dearborn, Department of Mathematics, Spring 2018 
	\item Braden Balentine, Department of Mathematics, Fall 2017 
	\item Noah Williams, Department of Mathematics, Fall 2016 (advisor) 
	\item Saeed Khalili, Department of Mathematics, Fall 2016 
	\item Ian Long, Department of Mathematics, Fall 2015 
	\item Natalie Coston, Department of Mathematics, Fall 2015 (advisor)
	\item Kathleen Smith, Department of Mathematics, Fall 2014

\end{itemize}


%\begin{itemize}
%	\item Member of Ph.D. thesis committees for Ian Long (Fall 2017), Peter Willis (Applied Mathematics, Spring 2018), Natalie Coston (Spring 2018), Noah Williams (Spring 2019), Saeed Khalili (Fall 2019), and Zhenhua Wang (Spring 2020).  
%	\item Member of master's defense and examination committees for Xiaorong Lie (Spring 2016), Patrick Normile (Spring 2016), Brendt Gerics (Spring 2018), Kellin Pelrine (Spring 2018), Isabel Corona (Spring 2018), Shumin Zeng (Fall 2018), and Richard Dyer (Fall 2018).  
%	\item Member of undergraduate honors thesis committees for Manna Chen (Economics, Spring 2016), Megan Sochinski (Spring 2018), Poramate Nakkirt (Fall 2019), and Megan Collins (Spring 2020). 
%	\item Member of comprehensive examination committees for Katy Smith (Fall 2014), Natalie Coston (Fall 2015), Ian Long (Fall 2015), Saeed Khalili (Fall 2016), Noah Williams (Fall 2016), Braden Balentine (Fall 2017), Krisztina Dearborn (Spring 2018), Albany Thompson (Fall 2018), Andrew Campbell (Spring 2019), and Zhe Feng (Electrical, Computer and Energy Engineering, Fall 2019). 
%\end{itemize}

\subsection*{Special Session and Summer School Organization}
\begin{itemize}
	\item Co-organizer of the workshop ``Random Polynomials and their Applications'' at the Institute for Computational and Experimental Research in Mathematics (ICERM), August 2025. 
	\item Co-organizer of the special session ``Random Matrices and Free Probability Theory'' at the 2024 Rocky Mountain Section meeting of the MAA, April 2024. 
	\item Co-organizer of the Summer School on Random Matrix Theory and Its Applications at the Ohio State University, May 2023. 
	\item Co-organizer of the AMS Special Session on Random Matrix Theory and its Applications at the 2022 Joint Mathematics Meetings, April 2022.
	\item Co-organizer of the AMS Special Session on Random Polynomials and Related Models at the 2022 Joint Mathematics Meetings, April 2022. 
	\item Co-organizer of the Special Session ``Random matrices and integrable systems'' at the 2020 Joint Mathematics Meetings, January 2020.  
	\item Organizer of the Contributed Session ``Random matrices'' at the $41$st Stochastic Processes and their Applications Conference, July 2019.
	\item Co-organizer of the Special Session ``Random matrices, integrable systems, and applications'' at the AMS Fall Western Sectional Meeting, October 2016.
	\item Co-organizer of the mini-symposium ``Randomness in Spectral Analysis'' at the SIAM Conference on Applied Linear Algebra, October 2015.
\end{itemize}
\subsection*{Referee} 
\begin{itemize}
	\item Member of grant review panel for the National Science Foundation, October 2022. 
	\item Ad hoc expert reviewer for National Science Foundation, March 2024. 
	\item Reviewer for Israel Science Foundation, March 2022, March 2023, and March 2024.  
	\item Reviewer for Swiss National Science Foundation, April 2020.  
	\item Referee for the following journals and conferences: 
	\begin{itemize}
		\item Annales de l'Institut Henri Poincar\'{e}, Probabilit\'{e}s et Statistiques
		\item Annals of Applied Probability
		\item Annals of Statistics
		\item Bernoulli Journal
		\item Communications in Contemporary Mathematics
		\item Communications in Mathematical Physics
		\item Discrete Mathematics
		\item Duke Mathematical Journal
		\item Electronic Communications in Probability
		\item Electronic Journal of Probability
		\item EPL (Europhysics Letters)
		\item Forum of Mathematics, Sigma
		\item Geometric And Functional Analysis (GAFA)
		\item International Mathematics Research Notices
		\item Israel Journal of Mathematics 
		\item Journal of Mathematical Analysis and Applications
		\item Journal of Mathematical Physics
		\item Journal of Statistical Physics
		\item Journal of Statistical Planning and Inference
		\item Journal of Theoretical Probability
		\item Linear Algebra and its Applications
		\item Potential Analysis
		\item Probability Surveys
		\item Probability Theory and Related Fields
		\item Proceedings of the American Mathematical Society
		\item Proceedings of Symposia in Applied Mathematics
		\item Random Matrices: Theory and Applications
		\item SIAM Journal on Matrix Analysis and Applications (SIMAX)
		\item Statistics \& Probability Letters
		\item Transactions of the American Mathematical Society
	\end{itemize}
\end{itemize}

\subsection*{Outside Thesis Committees}
\begin{itemize}
	%\item Outside Ph.D. thesis reader for Jean Rochet (Paris Descartes University, Spring 2016), Oanh Nguyen (Yale University, Spring 2017), Alk\'{e}os Micha\"{i}l (Paris Descartes University, Spring 2018), and Andrei Florin Deneanu (Yale University, Spring 2019).   
	\item Andrei Florin Deneanu, Applied Mathematics, Yale University, Spring 2019 (Ph.D. thesis reader)
	\item  Alk\'{e}os Micha\"{i}l, Applied Mathematics, Paris Descartes University, Spring 2018 (Ph.D. thesis reader)
	\item Oanh Nguyen, Mathematics, Yale University, Spring 2017 (Ph.D. thesis reader)
	\item Jean Rochet, Applied Mathematics, Paris Descartes University, Spring 2016 (Ph.D. thesis reader)
\end{itemize}

\subsection*{Outreach Talks} 
\begin{itemize}
\item Invited talk at the University of Colorado Boulder Math Club, October 2019
\item Invited talk at the Colorado Academy Math Club, December 2018
\item Invited talk at the Colorado Academy Math Club, December 2017
\item Invited talk at the University of Colorado Boulder Math Club, November 2016
\end{itemize}

\subsection*{Graduate Student Mentoring}
\begin{itemize}
\item Mentor to the following incoming graduate students: Zhenhua Wang (AY 2015--2016), Ian Miller (AY 2018--2019), Spencer Shortt (AY 2020--2021), Wilson Wu (AY 2023--2024), Storey Peacock (AY 2024--2025).  
\end{itemize}

\section*{Professional Development Activities}
\subsection*{University of Colorado Boulder}
\begin{itemize}
	\item Faculty Teaching Excellence Program (FTEP): Flipping the Class for the Skeptic, December 2019
	\item Faculty Teaching Excellence Program (FTEP): Designing a Syllabus for an Effective \& Flexible Course, August 2018
	\item First Year Seminar Training, June 2018 and August 2020.  
	\item Tenure and Promotion Workshops, October 2016, April 2018, and May 2020 
	\item Faculty Teaching Excellence Program (FTEP) Summer Assessment Institute: Achieving Course Goals: Gathering Evidence About Student Learning, May 2015
	\item New Faculty Orientation, August 2014
\end{itemize}


\section*{Technical Skills}
\begin{itemize}
	\item C, C++, \LaTeX, Linux, HTML/CSS, MATLAB, Python, Rust.
\end{itemize}

\bigskip

% Footer
\begin{center}
\begin{footnotesize}
Last updated: \today \\
\href{http://math.colorado.edu/~seor3821/}{\tt http://math.colorado.edu/\char`\~
seor3821/}
\end{footnotesize}
\end{center}
\end{document}
